\( \tool \): JavaScript IR-based Semantics Extraction Toolchain

### 2020-04-13 ase20/compiler.tex
[ASE] Slightly revised Section 4

\subsection{Token AST Converter}
\textit{Conversion rules} describe how to generate an \( \ires \) function for a
given token AST.  Each conversion rule is defined with its corresponding parsing
rule.  For basic parsing rules, their conversion rules always return the string
values of the contents in parsed tokens.  For example, the following conversion
rules are the omitted parts in the previous example for the step 5 of
\textbf{Evaluation}:
\begin{lstlisting}[style=myScalastyle]
// statements
val Stmt = ... ^^ { case _ ~ e ~ _ => IExpr(e) }
// expressions
val Expr =
  // codes      // false literal
  ... ^^ EStr | ... ^^ { _ => EBool(false) }            |
  // variables  // additions
  ... ^^ EId  | ... ^^ { case x ~ _ ~ y => EAdd(x, y) } |
  // function calls
  ... ^^ { case x ~ _ ~ y ~ _ => ECall(x, y) }
)
\end{lstlisting}
The conversion rule of the \code{Stmt} compile rule uses only the second sub
tree and constructs an \code{IExpr} \( \ires \) instruction.  For the second
sub-tree, the conversion rule of the fourth \code{Expr} compile rule is
applied. It constructs \code{ECall} \( \ires \) expression with the string value
of the first sub-tree and the sequence of the expressions of the third sub-tree.
In this way, the step 5 of \textbf{Evaluation} is converted to the following \(
\ires \) instruction:
\begin{lstlisting}[style=ires]
(Set array "length" (ToUint32 (+ padding len)) false)
\end{lstlisting}

@@

ECMAScript describes data types with several fields and methods used in the
specification.  Their methods are abstract algorithms but their semantics are
slightly different with other. They implicitly get their receiver objects as
arguments at callsites.  To mimic such implicit behavior, we added a special
variable \( \code{this} \) as the first parameter of a method, and passed a
receiver object at its callsite by modifying \textsf{Algorithm Compiler}.  For
example, an Environment Record type has the \textsf{DeleteBinding (N)} method.
Then, it gets two parameters, the special parameter \( \code{this} \) and normal
one \( \code{N} \).  Thus, the method call
\raisebox{-0.65ex}{\includegraphics[width=0.17\textwidth]{img/method-call.png}}
is compiled into the \( \ires \) instruction: \code{(DclRec.DeleteBinding
DclRec, N)}

>>>>

\subsection{Token AST Converter}
\textit{Conversion rules} describe how to generate an \( \ires \) function for a
given token AST.  Each conversion rule is defined with its corresponding parsing
rule.  For basic parsing rules, their conversion rules always return the string
values of the contents in parsed tokens.  For example, the following conversion
rules are the omitted parts in the previous example for the step 5 of
\textbf{Evaluation}:
\begin{lstlisting}[style=myScalastyle]
// statements
val Stmt = ... ^^ { case _ ~ e ~ _ => IExpr(e) }
// expressions
val Expr =
  // codes      // false literal
  ... ^^ EStr | ... ^^ { _ => EBool(false) }            |
  // variables  // additions
  ... ^^ EId  | ... ^^ { case x ~ _ ~ y => EAdd(x, y) } |
  // function calls
  ... ^^ { case x ~ _ ~ y ~ _ => ECall(x, y) }
)
\end{lstlisting}
The conversion rule of the \code{Stmt} compile rule uses only the second sub
tree and constructs an \code{IExpr} \( \ires \) instruction.  For the second
sub-tree, the conversion rule of the fourth \code{Expr} compile rule is
applied. It constructs \code{ECall} \( \ires \) expression with the string value
of the first sub-tree and the sequence of the expressions of the third sub-tree.
In this way, the step 5 of \textbf{Evaluation} is converted to the following \(
\ires \) instruction whose beautified form is the sixth line of the function
body in Figure~\ref{fig:array-literal-eval}.
\begin{lstlisting}[style=ires]
IExpr(ECall(EId("Set"), List(
  EId(array), EStr("length"), ECall(EId(ToUint32), List(
    EAdd(EId("padding"), EId("len")))), EBool(false))))
\end{lstlisting}

@@

ECMAScript describes data types with several fields and methods used in the
specification.  Their methods are abstract algorithms but their semantics are
slightly different with other. They implicitly get their receiver objects as
arguments at callsites.  To mimic such implicit behavior, we added a special
variable \( \code{this} \) as the first parameter of a method, and passed a
receiver object at its callsite by modifying \textsf{Algorithm Compiler}.  For
example, an Environment Record type has the \textbf{DeleteBinding (N)} method.
Thus, the corresponding \( \ires \) function has two parameters, the special
parameter \( \code{this} \) and normal one \( \code{N} \) and the method call
\raisebox{-0.65ex}{\includegraphics[width=0.17\textwidth]{img/method-call.png}}
in an abstract algorithm is compiled to the \( \ires \) instruction:
\code{(DclRec.DeleteBinding DclRec N)}
